The binary liquid model for gravity-driven microchannel simulations

### 2010-10-22 Text/paper.tex
Finished the wall gradient stuff. Moving to the grid refining.

After resolving the interface one can  calculate the
  velocity from the capillary number as:
  \begin{equation}
  U_{bubble}=0.005 \frac{\gamma}{\mu_{slug}}=0.005
\frac{0.0377}{0.66666}=2.82\,10^{-4},
  \end{equation}
  where $\mu_{slug}=1/3 (2.5-0.5)=0.6666$.
  This velocity implies the following pressure gradient calculated from the
  Poisuielle flow solution:
  \begin{equation}
  \begin{aligned}
  &U_{bubble}=\frac{H^2}{8\mu} \frac{\mathrm{d}P}{\mathrm{d}x}=\frac{Ny^2}{8/3
  (\tau_{liq}-1/2)}\frac{\mathrm{d}P}{\mathrm{d}x}\\
  &\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{Ny^2}\gamma Ca
  \end{aligned}
  \end{equation}
  Therefore the pressure gradient established is the following:
  \begin{equation}
  \begin{aligned}
  \frac{\mathrm{d}P}{\mathrm{d}x}=9.42\, 10^{-9}.
  \end{aligned}
  \end{equation}
  Note that in the case of large grids  height resolution is directly
involved in	
the physical time step as:
\begin{equation}
\Delta t =\frac{U_{LBM}}{U_{phys}} \Delta x ,
\end{equation}
where for example the real velocities in the physical world can reach
approximately $1$ m/s and physical channel height upto $1$ mm. In this case one
can easily approximate the physical time step:
\begin{equation}
\Delta t = 7.05 \, 10^{-10} \,\mathrm{s}
\end{equation}
which is a small time step. The typical simulation needs approximately
{\color{red} $100,000$} time steps to come to the steady state solution.

@@

\subsection{The influence of the wall gradient}
The results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$. This
section is to examine the wall gradient influence on simulations. We take large
enough resolution for simulations to be consistent. Simulation domain was
chosen as $177\mathrm{x}2626$ and the initial film width as
$12$ lattice boltzmann units, which correspond to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
{\color{red} Change these numbers $0.0709130255276, 0.0708903443305,
0.0708661222722,
0.0708369188112, 0.0707962325316, 0.0707266326981, 0.0705839443249,
0.0702489349415, 0.0697553433989$}. For the wall gradients $0.8$ and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles} The negative values of the phase gradient are
preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$. In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one. {\color{red} Michal, if you want to add some pictures go ahead
with it}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see if the width
is properly resolved then the wettability of the wall doesn't play any role
affecting the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}
\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.

>>>>

After resolving the interface one can  calculate the
  velocity from the capillary number as:
  \begin{equation}
  U_{bubble}=0.005 \frac{\gamma}{\mu_{slug}}=0.005
\frac{0.0377}{0.66666}=2.82\,10^{-4},
  \end{equation}
  where $\mu_{slug}=1/3 (2.5-0.5)=0.6666$.
  This velocity implies the following pressure gradient calculated from the
  Poisuielle flow solution:
  \begin{equation}
  \begin{aligned}
  &U_{bubble}=\frac{H^2}{8\mu} \frac{\mathrm{d}P}{\mathrm{d}x}=\frac{Ny^2}{8/3
  (\tau_{liq}-1/2)}\frac{\mathrm{d}P}{\mathrm{d}x}\\
  &\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{Ny^2}\gamma Ca
  \end{aligned}
  \end{equation}
  Therefore the pressure gradient established is the following:
  \begin{equation}
  \begin{aligned}
  \frac{\mathrm{d}P}{\mathrm{d}x}=9.42\, 10^{-9}.
  \end{aligned}
  \end{equation}
  Note that in the case of large grids  height resolution is directly
involved in	
the physical time step as:
\begin{equation}
\Delta t =\frac{U_{LBM}}{U_{phys}} \Delta x ,
\end{equation}
where for example the real velocities in the physical world can reach
approximately $1$ m/s and physical channel height upto $1$ mm. In this case one
can easily approximate the physical time step:
\begin{equation}
\Delta t = 7.05 \, 10^{-10} \,\mathrm{s}
\end{equation}
which is a small time step. The typical simulation needs approximately
$100000-300000$ time steps to come to the steady state solution giving the
physical time simulation around $10^{-5}--10^{-4}\,\mathrm{s}$, which is
probably not enough to find desired correlations.

@@

\subsection{The influence of the wall gradient}
The results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$. This
section is to examine the wall gradient influence on simulations. We take large
enough resolution for simulations to be consistent. Simulation domain was
chosen as $177\mathrm{x}2626$ and the initial film width as
$12$ lattice boltzmann units, which correspond to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
$0.0633$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0634$,$0.0633$,$0.0632$,
$0.0631$. The results are different in 4th digit. For the wall gradients $0.8$
and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles} The negative values of the phase gradient are
preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$ and do not interact
with the bubble which has phase value $-1$.  In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see if the width
is properly resolved then the wettability of the wall doesn't play any role
affecting the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}
\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.
